Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
ASSR: reformulate results for MFCCs, small correction to section VI, add best result for ob-c in section VII.B

Given a set of $d$-dimensional feature vectors $x_l^u\in X_u$, $l=[1,2,\ldots,L]$, extracted from the scene $s_u$, $u=[1,2,\ldots,U]$, the goal of KMeans is to partition $X_u$ into $M$ clusters $c^u_m\in C_u$, $m=[1,2,\ldots,M]$. The partitioning is done by minimizing for each $m$ cluster the squared error between its empirical mean (centroid) and the points it contains. Given $\mu_m^u$ the centroid of the cluster $c_m^u$, KMeans minimizes the following objective function:

@@

The similarity between all the scene centroids $\mu_i$, $i=[1,2,\ldots,I]$ with $I=UM$, is computed using a radial basis function (RBF) kernel $K$ combined with the local scaling method proposed in \cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K_{ij} = \exp\left( - \dfrac{\Vert \mu_i - \mu_j \Vert^2}{\Vert \mu_i - \mu_{k,i} \Vert \Vert \mu_j - \mu_{k,j} \Vert} \right) 
\end{equation}

@@

From this it appears that, although the \emph{ob} approaches are able to better retrieve the similarities between close scenes compared to \emph{early}, they are of no help when considering distant scenes of the same class. This is may due to the fact that, at some point, the MFCCs fail to capture the discriminant information contained in the larger-scale modulations, thus making a centroids-based description useless, or even counterproductive when the centroids are not weighted.

@@

\subsubsection*{Early \vs late integration}
Late integration, \ie building a prediction by majority voting over $128$ local windows of duration $T=372\,\mathrm{ms}$, outperforms early integration, \ie classifying the acoustic scene with a global window of duration $T=24\,\mathrm{s}$.
This result suggests that, despite its discriminative power at fine scales, the scattering transform is unable to segregate distinct acoustic events beyond the scale of about one second.
Therefore, it is beneficial to regard the scattering transform as a mid-level descriptor of acoustic content, not as a high-level descriptor, and adopt a data-driven strategy for the temporal integration of acoustic events within one scene.
Surprisingly, although we ran an extensive number of experiments to formulate object-based clustering into a supervised setting for acoustic scene classification, none of them managed to outperform the baseline strategy in temporal integration, namely majority voting.

>>>>

Given a set of $d$-dimensional feature vectors $x_l^u\in X_u$, $l=\lbrace 1,2,\ldots,L\rbrace$, extracted from the scene $s_u$, $u=\lbrace1,2,\ldots,U\rbrace$, the goal of KMeans is to partition $X_u$ into $M$ clusters $c^u_m\in C_u$, $m=\lbrace 1,2,\ldots,M\rbrace$. The partitioning is done by minimizing for each $m$ cluster the squared error between its empirical mean (centroid) and the points it contains. Given $\mu_m^u$ the centroid of the cluster $c_m^u$, KMeans minimizes the following objective function:

@@

The similarity between all the scene centroids $\mu_i$, $i=\lbrace1,2,\ldots,I \rbrace$ with $I=UM$, is computed using a radial basis function (RBF) kernel $K$ combined with the local scaling method proposed in \cite{selfTuneManor2004}:
\begin{equation}
\label{eq:kc}
K_{ij} = \exp\left( - \dfrac{\Vert \mu_i - \mu_j \Vert^2}{\Vert \mu_i - \mu_{k,i} \Vert \Vert \mu_j - \mu_{k,j} \Vert} \right) 
\end{equation}

@@

From this it appears that, although the \emph{ob} approaches are able to better retrieve the similarities between close scenes compared to \emph{early}, they are of no help when considering distant scenes of the same class. This may be due to the fact that, at some point, the MFCCs fail to dissociate the discriminative events of a scene from the non-informative ones, thus making a centroid-based description useless, or even counterproductive when the centroids are not weighted/selected.

@@

\subsubsection*{Early \vs late integration}
Late integration, \ie building a prediction by majority voting over $128$ local windows of duration $T=372\,\mathrm{ms}$, outperforms early integration, \ie classifying the acoustic scene with a global window of duration $T=24\,\mathrm{s}$.
This result suggests that, despite its discriminative power at fine scales, the scattering transform is unable to segregate distinct acoustic events beyond the scale of about one second.
Therefore, it is beneficial to regard the scattering transform as a mid-level descriptor of acoustic content, not as a high-level descriptor, and adopt a data-driven strategy for the temporal integration of acoustic events within one scene.
Surprisingly, although we ran an extensive number of experiments to formulate object-based clustering into a supervised setting for acoustic scene classification, none of them managed to outperform the baseline strategy in temporal integration, namely majority voting. The best result was achieved by the \emph{ob-a} approach using log-compressed scattering, and was of 66\% (0.7).
